PCA

### 2019-12-20 analysis/02_PCA.Rmd
better pca tsne figure

```{r pca}
# pca
mypca <- prcomp(countData)
eig.val <- get_eigenvalue(mypca)
head(eig.val)

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))
mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)
mypcadf <- mypcadf %>% select(bird,sex,tissue,treatment,PC1:PC6)
head(mypcadf)

plotcolorfulpcs <- function(whichfactor, whichcolors){
  p <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = whichfactor)) +
    geom_point(size = 1)  +
    theme_B3() +
    theme(legend.title = element_blank(),
         axis.text = element_blank(),
         legend.position = "none") +
    labs(x = "PC1", y = "PC2") +
    scale_color_manual(values = whichcolors) 
  print(p)
}

@@

d <- fviz_screeplot(mypca, addlabels = TRUE, ylim = c(0, 50),  ncp = 5) + labs(title = NULL, y = "Variance") + theme_B3() 
e <- fviz_contrib(mypca, choice = "var", axes = 1, top = 5)  + labs(title = NULL, subtitle = "PC1", x = NULL) + 
          theme_B3() + theme(axis.text.x = element_text(angle = 55, hjust = 1))
f <- fviz_contrib(mypca, choice = "var", axes = 2, top = 5)  + labs(title = NULL, subtitle = "PC2", y = NULL, x = NULL) + 
          theme_B3()  + theme(axis.text.x = element_text(angle = 55, hjust = 1))
g <- fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 6)) + 
      theme_B3() + 
      labs(x = "PC1", y = "PC2", title =  NULL) +
      theme( axis.text = element_blank())

abc <- plot_grid(a,b, c, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
defg <- plot_grid(d,e,f,g, nrow = 1, rel_widths = c(1, 0.55, 0.45, 1), labels = c("h", "i", "j", "k" ), label_size = 12)
dg <- plot_grid(d,g, NULL, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
plot_grid(abc, defg, nrow = 2)
```

```{r tSNE}
# prep for tsne
euclidist <- dist(countData) # euclidean distances between the rows

@@

plotcolorfultsnes <- function(whichfactor, whichcolors){
  p <- ggplot(tsne_df_cols, aes(x = V1, y = V2, color = whichfactor)) +
    geom_point(size = 1) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank())
  print(p)
}

@@

hij <- plot_grid(h,i,j, nrow = 1, labels = c("a", "b", "c"), label_size = 12)
hij
```
```{r PCA-tSNE}
plot_grid(hij, abc, dg, nrow = 3)
```

>>>>

```{r pcadf}
# pca
mypca <- prcomp(countData)
eig.val <- get_eigenvalue(mypca)
head(eig.val)

mypcadf <- data.frame(PC1 = mypca$x[, 1], PC2 = mypca$x[, 2], PC3 = mypca$x[, 3], 
                  PC4 = mypca$x[, 4],PC5 = mypca$x[, 5],PC6 = mypca$x[, 6],
                  ID = row.names(countData))
mypcadf$V1 <- row.names(mypcadf)
mypcadf <- left_join(colData, mypcadf)
mypcadf <- mypcadf %>% select(bird,sex,tissue,treatment,PC1:PC6)
head(mypcadf)
```

```{r pca}
plotcolorfulpcs <- function(whichfactor, whichcolors){
  p <- ggplot(mypcadf, aes(x = PC1, y = PC2, color = whichfactor)) +
    geom_point(size = 1)  +
    theme_B3() +
    theme(legend.title = element_blank(),
         axis.text = element_blank(),
         legend.position = "none") +
    labs(x = "PC1", y = "PC2") +
    scale_color_manual(values = whichcolors) 
  print(p)
}

@@

d <- fviz_screeplot(mypca, addlabels = TRUE, ylim = c(0, 50),  ncp = 5, barcolor = "white", barfill = "white") + 
  labs(title = NULL, y = "PC Variance") + theme_B3() 
e <- fviz_contrib(mypca, choice = "var", axes = 1, top = 5)  + labs(title = NULL, subtitle = "PC1", x = NULL) + 
          theme_B3() + theme(axis.text.x = element_text(angle = 55, hjust = 1))
f <- fviz_contrib(mypca, choice = "var", axes = 2, top = 5)  + labs(title = NULL, subtitle = "PC2", y = NULL, x = NULL) + 
          theme_B3()  + theme(axis.text.x = element_text(angle = 55, hjust = 1))
g <- fviz_pca_var(mypca,  labelsize = 3 , axes.linetype = "blank", 
                   repel = TRUE ,
                  select.var= list(contrib = 6)) + 
      theme_B3() + 
      labs(x = "PC1", y = "PC2", title =  NULL) +
      theme( axis.text = element_blank())

legend <- png::readPNG("../figures/images/DoveParentsRNAseq_legend.png")
legend <-  grid::rasterGrob(legend, interpolate=TRUE)

abc <- plot_grid(a,b, c, nrow =  1,  labels = c("d", "e", "f"), label_size = 12)
defg <- plot_grid(d,e,f,g, nrow = 1, rel_widths = c(1, 0.55, 0.45, 1), labels = c("h", "i", "j", "k" ), label_size = 12)
dg <- plot_grid(d,g, legend, nrow = 1, rel_widths = c(1, 1, 1), labels = c("h", "i", NULL ), label_size = 12)
plot_grid(abc, dg, nrow = 2)
```

```{r tSNE-df}
# prep for tsne
euclidist <- dist(countData) # euclidean distances between the rows

@@

```

```{r tSNE}
plotcolorfultsnes <- function(whichfactor, whichcolors){
  p <- ggplot(tsne_df_cols, aes(x = V1, y = V2, color = whichfactor)) +
    geom_point(size = 1) +
    theme_B3() +
    labs(x = "tSNE 1", y = "tSNE 2") +
    scale_color_manual(values = whichcolors) +
    theme(legend.position = "none",
          axis.text = element_blank())
  print(p)
}

@@

hij <- plot_grid(h,i,j, nrow = 1, labels = c("a", "b", "c"), label_size = 12)
hij

```
```{r PCA-tSNE, fig.height= 7, fig.width=7}
plot_grid(hij, abc, dg, nrow = 3)

```
